Physics of Period Spacing Patterns

### 2023-07-06 notes/period_spacing/period_spacings.tex
minor typo fixes

So what happens when we get deviations from our beautiful straight lines, what's up with that? These occur due to abrupt shifts in the BV profile, sometimes referred to as buoyancy glitches \citep[e.g.,]{Cunha+2019}, which end up trapping particular modes in certain regions of the star. This means that certain modes end up getting shifted in period and moving away from the pattern.

@@

These same sharp features should occur after a star experiences mass transfer and so we might expect that the period spacing pattern bears some imprint of the stars previous mass transfer episode - we've got 4 more weeks to find out!

>>>>

So what happens when we get deviations from our beautiful straight lines, what's up with that? These occur due to abrupt shifts in the BV profile, sometimes referred to as buoyancy glitches \citep[e.g.,][]{Cunha+2019}, which end up trapping particular modes in certain regions of the star. This means that certain modes end up getting shifted in period and moving away from the pattern.

@@

These same sharp features should occur after a star experiences mass transfer and so we might expect that the period spacing pattern bears some imprint of the stars previous mass transfer episode - we've got 4 more weeks to find out if that's true and how it might look!
